Quality measure notes

### 2021-08-27 StateOfPractice/Ao-Report/16AnswersToResearchQuestions.tex
MI report - updated ch 6

This section answers our research questions in Section \ref{sec_research_questions}. The answers are based on our quality measurements and developer interviews. Sections \ref{sec_rq_artifacts}, \ref{sec_rq_tools}, \ref{sec_rq_PPM}, \ref{sec_rq_pain_points}, \ref{sec_rq_qualities}, and \ref{sec_rq_comparison} summarize the answers to the six questions respectively. Section \ref{sec_threats_to_validity} lists the threats to the validity of our research.

@@

Table \ref{tab_artifacts_frequency} shows the frequency of some artifacts in the 29 MI projects.

@@

\subsection{CI/CD Tools}
As mentioned in Section \ref{sec_result_correctness_verifiability}, we identified five projects using CI/CD tools. \textit{3D Slicer} and \textit{OHIF Viewer} used CircleCI; \textit{ImageJ}, \textit{Fiji}, and \textit{dwv} used Travis. According to the interviews with developers, \textit{dwv} and \textit{Weasis} used GitHub Actions.

\subsection{User Support Tools}
Table \ref{tab_user_support_model} shows the user support tools by the number of projects using them.

\subsection{Version Control Tools}
Briefly speaking, 27 of the 29 projects chose git as the version control tool, and 24 used GitHub to host the repositories. Section \ref{sec_score_maintainability} lists more details.

\subsection{Documentation Tools}
Table \ref{tab_doc_tools} lists the documentation tools by the number of answers from the interviewees.

\subsection{Contribution Management Tools}
Table \ref{tab_method_receive_contributions} shows the ways of receiving contributions by the number of answers from the interviewees.

\subsection{Project Management Tools}
Table \ref{tab_pm_tools} shows the tools for project management by the number of answers from the interviewees.

@@

\subsection{Software Testing}
As shown in Section \ref{fg_correctness_erifiability_scores}, we only identified the use of unit testing in less than half of the 29 projects. Most projects did not have requirements specifications and theory manuals.

@@

Table \ref{tab_q15_threats_correctness} lists a threat to \textit{correctness}: with huge datasets for testing, the tests are expensive and time-consuming. Table \ref{tab_q15_strategies_correctness} shows that three interviewees endorsed self tests / automated tests, which may save the time for testing.

@@

\subsection{Documentation}
Section \ref{fg_correctness_erifiability_scores} shows that most projects did not have requirements specifications and theory manuals. Table \ref{tab_maintainability_docs} presents which projects had a project plan, developer’s manual, or API documentation, which implies better \textit{maintainability}. Table \ref{tab_Visibility/Transparency_docs} lists the existing documents that can improve \textit{visibility/transparency} of the projects. Table \ref{tab_artifacts_frequency} reveals the number of all the artifacts in the 29 projects.

Most of the nine interviewees thought that documentation was essential to their projects. However, they hold the common opinion that their documentation needed improvements. Nearly half of them also believed that the lack of time prevented them from improving the documentation. See more details in Section \ref{sec_interview_documents}.

@@

We answer this question primarily by interviewing the developers. This section presents the pain points and the solutions from the developers and our team.

@@

\subsection{Solutions}
Section \ref{sec_interview_pain_points} lists the details about the potential and proven solutions from the developers in the MI domain. We also summarize our general recommendations on software development in all SC domains in Section \ref{ch_recommendations}.

@@

\subsection{Results by Measuring Software Qualities}
Section \ref{ch_results} contains our measurement results for \textit{Installability}, \textit{Correctness \& Verifiability}, \textit{Reliability}, \textit{Robustness}, \textit{Usability}, \textit{Maintainability}, \textit{Reusability}, \textit{Understandability}, and \textit{Visibility/Transparency}. We applied (surface) measurements to the nine qualities, and hope that the grading scores represent their current status. We believe that our assessments also revealed some of the development teams' practices addressing the qualities.

@@

Generally speaking, most of the top-ranking MI software projects also received greater attention and popularity on GitHub. Project \textit{dwv} was popular on GitHub, but we ranked it low. As mentioned in Section \ref{sec_result_installability}, we failed to build it locally, and used the test version on its websites for the measurements. We followed the instructions and tried to run the command ``yarn run test" locally, which did not work. In addition, the test version did not detect a broken DICOM file and displayed a blank image as described in Section \ref{sec_result_robustness}. We might underestimate the scores for \textit{dwv} due to uncommon technical issues.

\begingroup
\renewcommand{\arraystretch}{0.85}
\begin{table}[H]
\centering
\begin{tabular}{lllll}
\hline
Software & Our ranking & Stars/yr & Watch/yr & Forks/yr \\ \hline
3D Slicer & 1 & 284.25 & 18.75 & 128.25 \\
ImageJ & 2 & 83.58 & 9.37 & 30.00 \\
OHIF Viewer & 3 & 277.04 & 19.30 & 223.83 \\
Fiji & 4 & 44.20 & 4.98 & 20.68 \\
ParaView & 5 & 66.76 & 7.11 & 28.36 \\
Weasis & 6 & 36.00 & 5.10 & 18.90 \\
medInria & 7 & 7.04 & 3.35 & 6.35 \\
BioImage Suite Web & 8 & 17.85 & 4.62 & 6.77 \\
OsiriX Lite & 9 & 34.14 & 8.62 & 23.77 \\
INVESALIUS 3 & 10 & 39.66 & 4.11 & 17.37 \\
Gwyddion & 11 & n/a & n/a & n/a \\
Horos & 12 & 48.62 & 9.23 & 18.00 \\
SMILI & 13 & 3.04 & 0.91 & 1.52 \\
Ginkgo CADx & 14 & 18.83 & 4.43 & 5.72 \\
ITK-SNAP & 15 & 9.10 & 0.97 & 3.59 \\
MicroView & 16 & 1.48 & 0.82 & 0.82 \\
Papaya & 17 & 44.70 & 4.84 & 19.71 \\
MRIcroGL & 18 & 23.63 & 3.38 & 3.38 \\
XMedCon & 19 & n/a & n/a & n/a \\
Slice:Drop & 20 & 9.73 & 2.16 & 4.97 \\
DicomBrowser & 21 & n/a & n/a & n/a \\
AMIDE & 22 & n/a & n/a & n/a \\
dwv & 23 & 123.56 & 11.59 & 51.36 \\
3DimViewer & 24 & n/a & n/a & n/a \\
GATE & 25 & 18.90 & 5.79 & 25.79 \\
dicompyler & 26 & 35.18 & 4.77 & 13.64 \\
Drishti & 27 & 16.04 & 3.78 & 4.43 \\
MatrixUser & 28 & 2.00 & 0.33 & 0.33 \\
DICOM Viewer & 29 & 42.86 & 5.71 & 8.57 \\ \hline
\end{tabular}
\caption{\label{tab_ranking_vs_GitHub}Software ranking versus GitHub metrics}
\end{table}
\endgroup

@@

An example of interpreting Table \ref{tab_top_software_vs_experts} is as follows: in row 2, \textit{ImageJ} has rank 2 by our assessment, and the number \textit{(3)} means that it has rank 3 by the experts; likewise, \textit{Horos} has rank 2 by domain expers, and rank 12 by our assessment.

@@

As mentioned in Section \ref{sec_mi_software_selection}, six of the recommended software packages did not have Visualization as the primary function, so we did not include them on our final list.

@@

\begin{enumerate}
\item We compared nine software qualities for 29 software packages, so we could only spend a limited time on each of them. As a result, our assessments may not be thorough in revealing their status fully.
\item We used the grading template in Appendix \ref{ap_grading_template} to guide our measurements. Our impressions of the software - such as user experience - were factors in deciding some scores. Thus, there is a risk that some scores may be subjective and biased.
\item It was not practical to ask each development team for every piece of information. We collected much information - such as artifacts and funding situations of software - by ourselves. There may be cases that we missed some information.
\item We interviewed eight teams, which is a good proportion of the 29. However, there is still a risk that they might not well represent the whole MI software community.
\item As mentioned in Section \ref{ch_interview}, one interviewee was too busy to participate in a full interview, so he provided a version of written answers to us. Since we did not have the chance to explain our questions or ask him follow-up questions, there is a possibility of misinterpretation of the questions or answers.
\item As mentioned in Section \ref{sec_rq_comparison}, we gave \textit{dwv} much lower scores than its GitHub popularity. We might underestimate its rank due to uncommon technical issues.
\end{enumerate}

>>>>

This section answers our research questions from Section \ref{sec_research_questions}. The answers are based on our quality measurements and developer interviews. Sections \ref{sec_rq_artifacts}-- \ref{sec_rq_comparison} summarize the answers to the six questions, respectively. Section \ref{sec_threats_to_validity} lists the threats to the validity of our research.

@@

As mentioned in Section \ref{sec_grading_template}, we search for all the artifacts in a project when measuring \textit{maintainability}. The detailed records of the existing artifacts in the 29 MI projects are at \hyperlink{https://data.mendeley.com/datasets/k3pcdvdzj2/1}{https://data.mendeley.com/datasets/k3pcdvdzj2/1}. Table \ref{tab_artifacts_frequency} summarizes the frequency of the artifacts .

@@

\subsection{CI/CD Tools}
As mentioned in Section \ref{sec_result_correctness_verifiability}, we identified five projects using CI/CD tools. \textit{3D Slicer} and \textit{OHIF Viewer} used CircleCI; \textit{ImageJ}, \textit{Fiji}, and \textit{dwv} used Travis. We identified the above projects and tools by examining the documentation and source code of all projects. Thus, we may missed some projects or tools. According to the interviews with developers, \textit{dwv} and \textit{Weasis} used GitHub Actions.

\subsection{User Support Tools}
Table \ref{tab_user_support_model} shows the user support tools by the number of projects using them. The two most popular tools are GitHub issue and FAQ.

\subsection{Version Control Tools}
Briefly speaking, 27 of the 29 projects chose git as the version control tool, and 24 used GitHub to host the repositories. Section \ref{sec_score_maintainability} provides more details.

\subsection{Documentation Tools}
Table \ref{tab_doc_tools} lists the documentation tools by the number of answers from the interviewees. The two most popular tools are forum discussions and videos.

\subsection{Contribution Management Tools}
Table \ref{tab_method_receive_contributions} shows the ways of receiving contributions by the number of answers from the interviewees. All eight development teams were using GitHub with pull requests as the tool. The most popular tool in the past was email.

\subsection{Project Management Tools}
Table \ref{tab_pm_tools} shows the tools for project management by the number of answers from the interviewees. GitHub was the top-chosen tool.

@@

\subsection{Software Testing}
As shown in Section \ref{fg_correctness_erifiability_scores}, we identified the use of unit testing in less than half of the 29 projects.

@@

Table \ref{tab_q15_threats_correctness} lists a threat to \textit{correctness}: with huge datasets for testing, the tests are expensive and time-consuming. Table \ref{tab_q15_strategies_correctness} shows that three interviewees endorsed self tests / automated tests, which may save time for testing.

@@

\subsection{Documentation}
Section \ref{fg_correctness_erifiability_scores} shows that all projects did not have theory manuals. We identified a road map in the \textit{3D Slicer} project, and no requirements specifications for the rest. Table \ref{tab_maintainability_docs} presents which projects had a project plan, developer’s manual, or API documentation, which implies better \textit{maintainability}. Table \ref{tab_Visibility/Transparency_docs} lists the existing documents that can improve \textit{visibility/transparency} of the projects. Table \ref{tab_artifacts_frequency} reveals the number of all the artifacts in the 29 projects.

Eight of the nine interviewees thought that documentation was essential to their projects. However, they hold the common opinion that their documentation needed improvements. Nearly half of them also believed that the lack of time prevented them from improving the documentation. See more details in Section \ref{sec_interview_documents}.

@@

We answer this question primarily by interviewing the developers. This section presents the pain points and the solutions proposed by the developers.

@@

\subsection{Solutions}
Section \ref{sec_interview_pain_points} lists the details about the potential and proven solutions from the developers in the MI domain.

@@

\subsection{Results by Measuring Software Qualities}
Section \ref{ch_results} contains our measurement results for \textit{Installability}, \textit{Correctness \& Verifiability}, \textit{Reliability}, \textit{Robustness}, \textit{Usability}, \textit{Maintainability}, \textit{Reusability}, \textit{Understandability}, and \textit{Visibility/Transparency}. We applied (surface) measurements to the nine qualities, and hope that the grading scores represent their current status.

@@

Generally speaking, most of the top-ranking MI software projects also received greater attention and popularity on GitHub. Project \textit{dwv} was popular on GitHub, but we ranked it low. As mentioned in Section \ref{sec_result_installability}, we failed to build it locally, and used the test version on its websites for the measurements. We followed the instructions and tried to run the command ``yarn run test" locally, which did not work. In addition, the test version did not detect a broken DICOM file and displayed a blank image as described in Section \ref{sec_result_robustness}. We might underestimate the scores for \textit{dwv} due to uncommon technical issues. We also ranked \textit{DICOM Viewer} much lower than its popularity. As mentioned in Section \ref{sec_result_installability} it depended on the NextCloud platform that we could not successfully install. Thus, we might underestimate the scores of its \textit{surface reliability} and \textit{surface robustness}. We weighted all qualities equally, which is not likely to be the case with all end-users. As a result, some projects may have received higher popularity because of their better performance in part of the nine qualities.

\begingroup
\renewcommand{\arraystretch}{0.85}
\begin{table}[H]
\centering
\begin{tabular}{lllll}
\hline
Software & Our ranking & Stars/yr & Watches/yr & Forks/yr \\ \hline
3D Slicer & 1 & 284.25 & 18.75 & 128.25 \\
OHIF Viewer & 3 & 277.04 & 19.3 & 223.83 \\
dwv & 23 & 123.56 & 11.59 & 51.36 \\
ImageJ & 2 & 83.58 & 9.37 & 30 \\
ParaView & 5 & 66.76 & 7.11 & 28.36 \\
Horos & 12 & 48.62 & 9.23 & 18 \\
Papaya & 17 & 44.7 & 4.84 & 19.71 \\
Fiji & 4 & 44.2 & 4.98 & 20.68 \\
DICOM Viewer & 29 & 42.86 & 5.71 & 8.57 \\
INVESALIUS 3 & 10 & 39.66 & 4.11 & 17.37 \\
Weasis & 6 & 36 & 5.1 & 18.9 \\
dicompyler & 26 & 35.18 & 4.77 & 13.64 \\
OsiriX Lite & 9 & 34.14 & 8.62 & 23.77 \\
MRIcroGL & 18 & 23.63 & 3.38 & 3.38 \\
GATE & 25 & 18.9 & 5.79 & 25.79 \\
Ginkgo CADx & 14 & 18.83 & 4.43 & 5.72 \\
BioImage Suite Web & 8 & 17.85 & 4.62 & 6.77 \\
Drishti & 27 & 16.04 & 3.78 & 4.43 \\
Slice:Drop & 20 & 9.73 & 2.16 & 4.97 \\
ITK-SNAP & 15 & 9.1 & 0.97 & 3.59 \\
medInria & 7 & 7.04 & 3.35 & 6.35 \\
SMILI & 13 & 3.04 & 0.91 & 1.52 \\
MatrixUser & 28 & 2 & 0.33 & 0.33 \\
MicroView & 16 & 1.48 & 0.82 & 0.82 \\
Gwyddion & 11 & n/a & n/a & n/a \\
XMedCon & 19 & n/a & n/a & n/a \\
DicomBrower & 21 & n/a & n/a & n/a \\
AMIDE & 22 & n/a & n/a & n/a \\
3DimViewer & 24 & n/a & n/a & n/a \\ \hline
\end{tabular}
\caption{\label{tab_ranking_vs_GitHub}Software ranking versus GitHub metrics}
\end{table}
\endgroup

@@

An example of interpreting Table \ref{tab_top_software_vs_experts} is as follows: in row 2, \textit{ImageJ} has rank 2 by our assessment, and the number \textit{(3)} means that it has rank 3 by the experts; likewise, \textit{Horos} has rank 2 by the domain experts, and rank 12 by our assessment.

@@

As mentioned in Section \ref{sec_mi_software_selection}, six of the recommended software packages did not have visualization as the primary function, so we did not include them on our final list.

@@

\begin{enumerate}
\item We compared nine software qualities for 29 software packages, so we could only spend a limited time on each of them. As a result, our assessments may have missed something relevant.
\item We used the grading template in Appendix \ref{ap_grading_template} to guide our measurements. Our impressions of the software - such as user experience - were factors in deciding some scores. Thus, there is a risk that some scores may be subjective and biased.
\item It was not practical to ask each development team for every piece of information. We collected much information - such as artifacts and funding situations of software - by ourselves. There may be cases that we missed some information.
\item Our ranking is partly based on surface (shallow) measurement, which may not fully reveal the underlying qualities.
\item We interviewed eight teams, which is a good proportion of the 29. However, there is still a risk that they might not well represent the whole MI software community.
\item As mentioned in Section \ref{ch_interview}, one interviewee was too busy to participate in a full interview, so he provided a version of written answers to us. Since we did not have the chance to explain our questions or ask him follow-up questions, there is a possibility of misinterpretation of the questions or answers.
\item As mentioned in Section \ref{sec_result_installability}, we could not install or build \textit{dwv}, \textit{GATE}, and \textit{DICOM Viewer}. We used a deployed online version for \textit{dwv}, a VM version for \textit{GATE}, but no alternative for \textit{DICOM Viewer}. We might underestimate their rank due to uncommon technical issues.
\item Our ranking gave all qualities equal weight, which may not be the case with all end-users. Thus, it may not represent the popularity of software among end-users.
\item The number of GitHub stars, watches, and forks are not perfect measures of popularity, but they are what we had available.
\end{enumerate}
